Modeling Human Interactions in Collaborative Interactive Evolutionary Computation

### 2017-04-06 2017-GECCO-Modeling-User-Interactions-in-IEC/paper-short-body.tex
Project codes

\begin{acks}
This work has been supported in part by: de Ministerio espa\~{n}ol de Econom\'{\i}a y Competitividad under project TIN2014-56494-C4-{1,2,3}-P (UGR-EPHEMECH), by Consejo Nacional de Ciencia y Tecnolog\'{\i}a under project 220590, and by Junta de Extremadura FEDER, project GR15068

>>>>

\begin{acks}
This work has been supported in part by: de Ministerio espa\~{n}ol de Econom\'{\i}a y Competitividad under project TIN2014-56494-C4-\{1,2,3\}-P (UGR-EPHEMECH), by Consejo Nacional de Ciencia y Tecnolog\'{\i}a under project 220590, and by Junta de Extremadura FEDER, project GR15068
